---
title: Using the `depstats` package
author: Ivan Muyun Zou
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{foreach}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{utf8}
---

```{r loadLibs, include=FALSE}
library(depstats)
```

## Dependence Structures
Many dependence structures are available in the package. The generated sample can be immediately inspected with `qplt()` function.

```{r 1, fig.width=7.25, fig.height=5}
set.seed(0)
par(mfrow = c(1, 2),
    oma = c(5,4,0,0) + 0.25,
    mar = c(0,0,1,1) + 0.25)
n = 100 #sample size
qplt(diam.cld(n)) #Diamond
qplt(cross.cv(n)) #Cross
```

More manipulations are available. In the following, we generated a dependent sample of sample size 200 from Cubic structure with normal noises imposed on top while the level of noise itself is sampled from a uniform (0, 0.1) distribution.

```{r 2, fig.width=7, fig.height=5}
set.seed(0)
n = 200 #sample size
X <- normnoise(cubic.cv(n),runif(1,0,0.1))
qplt(X)
```

Many samples may be needed which can be easily addressed with `depgen()` function. In the following, 2 samples are generated while random rotations are applied.

```{r 3, fig.width=7.25, fig.height=5}
set.seed(0)
par(mfrow = c(1, 2),
    oma = c(5,4,0,0) + 0.25,
    mar = c(0,0,1,1) + 0.25)
n = 200 #sample size

```

## Image Greyscale Pixels
The generated bivariate random samples can generate 2-dimensional density plots.  

```{r 4, fig.width=7, fig.height=5}
set.seed(0)
par(mfrow = c(1, 2),
    oma = c(5,4,0,0) + 0.25,
    mar = c(0,0,1,1) + 0.75)
n = 200 #sample size
X <- normnoise(parabola.cv(n),0.05)
qplt(X)
IMAGE <- sampleapply(X,c(n),0,grid=25)
image(matrix(IMAGE,nrow=25,byrow=T))
```

## Experiment Result Evaluation

Power plots can be obtained from function `plotpowers()`. Power data are readily available in the package.

```{r 5, fig.width=7, fig.height=5}
par(mfrow = c(2, 2),
    oma = c(5,4,0,0) + 0.75,
    mar = c(0,0,1,1) + 1.75)

Linear <- depPowers[1+c(0,20,40,60,80,100),]
plotpowers(Linear,'Linear')
Diamond <- depPowers[2+c(0,20,40,60,80,100),]
plotpowers(Diamond,'Diamond')
Triangle <- depPowers[3+c(0,20,40,60,80,100),]
plotpowers(Triangle,'Triangle')
Crescent <- depPowers[4+c(0,20,40,60,80,100),]
plotpowers(Crescent,'Crescent')
```

Alternatively, we may inspect the results in a table.

```{r 6}
PowersSummary <- powerssummary(depPowers)
head(PowersSummary[,1:5])
```



